How to Write Theses\\ With Two Line Titles

### 2019-08-04 chapters/introduction/introduction.tex
Updates from Overleaf

In this study we will answer the following research questions:
\begin{enumerate}
  \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
  %\item Can we quantify reliability of predictions made by machine learning algorithms?
  \item How sensitive are the predictions made by ML algorithms to the change in input data?
  \item At what point does the algorithm fail to produce correct classifications on distorted inputs?
\end{enumerate}
%Point of failure. by humans& computer. (visual inpection)
%Properties of ML affect
%

>>>>

In this study we will answer the following research questions:
\begin{enumerate}
%   \item How does metamorphic testing compare to other testing methodologies for testing machine learning algorithms?
  %\item Can we quantify reliability of predictions made by machine learning algorithms?
  \item Identifying metamorphic properties that can be used to generate new test data from image datasets.
%   \item How does metamorphic properties affect different dataset and deep-learning algorithms?
  \item Robustness of the deep learning algorithms to the identified metamorphic properties?
  \item What range of Metamorphic properties identified is most useful while generating new test cases.
%   \item How sensitive are the predictions made by ML algorithms to the change in input data?
%   \item At what point does the algorithm fail to produce correct classifications on distorted inputs?

\end{enumerate}
%Point of failure. by humans& computer. (visual inpection)
%Properties of ML affect
%

### 2019-08-04 chapters/litReview/finalLit.tex
Updates from Overleaf

% \section{Software testing}
% Testing is an essential activity in software engineering. In the simplest terms, it amounts to observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions. Testing is widely used in industry for quality assurance. Software testing is a broad term encompassing a wide spectrum of different activities, from the testing of a small piece of code by the developer (unit testing), to the customer validation of a large information system (acceptance testing), to the monitoring at run-time of a network-centric service-oriented application.
\section{Testing in the Presence of Uncertainty \cite{Elbaum2014}}
Uncertainty is present in most systems that are built today, whether introduced by human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, uncertainty increases the ambiguity of what constitutes the input space and what is deemed as acceptable behavior, which are two key attributes of a test. In this paper, the authors explore the potential directions for dealing with uncertainty during testing.
Two ways to deal with uncertainty are to exercise more control over the inputs provided to the unit under test and to constrain the testing environment. Some uncertainties like those present in systems that deal with the physical world are aleatoric; that is, they cannot be known precisely because of their inherent variability and noise. Epistemic uncertainties are those that could be resolved with enough effort (e.g., over-engineering a sensor-based system to minimize inference errors about the environment)— and resolving them are becoming more numerous and costly, as the systems are becoming increasingly complex. A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time. The authors provide a set of requirements for adequate handling of uncertainty in testing:
\begin{enumerate}
  \item Specifying input distributions and generating inputs with the help of the distributions instead of using discrete inputs.
  \item Probabilistic oracles that can help distinguish acceptable from unacceptable misbehaviors. These models will also provide the specification of the likelihood of results.
  \item Richer models to represent system and environment uncertainty, so that uncertainties can be connected to test requirements and outcomes. This will help with automated uncertainty quantification.
\end{enumerate}
Not all systems will impose these requirements, and not all techniques will satisfy them. In fact, they expect it will be necessary to develop a suite of techniques for dealing with uncertainty, selected according to system characteristics and the particular forms of uncertainty the system embodies and based on the use of stochastic models and quantitative analyses.

\section{On Testing Non-testable Programs \cite{Weyuker}}
The current testing research activities fall into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}
An oracle is a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts. Programs for which such oracles do not exist are called 'non-testable'. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.
Non-testable programs can be usually classified into three categories:
\begin{enumerate}
  \item Programs that were written to determine the correct answer.
  \item Programs that produce a lot of outputs such that it is hard to verify all of them.
  \item Programs where tester have a misconception (tester believes that he has the oracle even though he might not).
\end{enumerate}
In absence of oracles, the ideal way to test a program is through Pseudo Oracles/Dual Coding. But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation. A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors.
Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}
Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer. In such cases, we make use of partial oracles. It is relatively easier to test the systems on simpler inputs for which the output is known. There is rarely a single correct answer in these types of computations. Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution. The authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

>>>>

\section{Software testing}
Testing is one of the most important activity in software development life cycle. Bertolino define software testing as, "observing the execution of a software system to validate whether it behaves as intended and identify potential malfunctions". Testing is widely used in industry for quality assurance purposes. Software testing is an umbrella term that encompasses a wide range of different sub tasks, like unit testing a small piece of code developers, acceptance testing a large information system for customer validation, monitoring the application at run-time to ensure uninterrupted service. Some studies (B. Beizer) have estimated that software testing can use upto fifty percent, or more, of the total development cost. Thus, it is program software testing is worthy of our attention for research and improvement. 
Weyuker (1982) categorizes the testing research activities into three categories:
\begin{enumerate}
  \item Develop a sound theoretical basis for testing.
  \item Devise and improve testing methodologies, especially the mechanizable ones.
  \item Define accurate measurement criteria for testing data adequately.
\end{enumerate}

However,  there are a lot of uncertainties in program testing and it is often not so straightforward to test programs. These Uncertainties in most systems are introduced by either human decisions, machine learning algorithms, external libraries, or sensing variability mostly due to the need to support deep interactions between interconnected software systems and their users and execution environments. In the context of software testing, the two fundamental problems are: increased ambiguity of what constitutes the input space and what is deemed as acceptable behavior in absence of an oracle. (Chen, Tse, & Zhou Semi Proving: An integrated method and Elbaum2014)

 One of the first problems that testers run into is that they don't have access to acceptable output to test the program output against. This problem is often referred to as the Oracle problem. Weyuker (1982) provides founding definition of an oracle as a system that determines the correctness of the solution by comparing the system’s output to the one that it predicts. As per Weyuker, non-testable programs can be defined as the programs for which such oracles do not exist. The term non-testable is used, from the point of view of correctness testing. If one cannot decide whether or not the output is correct or have to spend some extraordinary amount of resources to do so, testing those systems may not be worth it.

 One way of elevating the oracle-problem is through the use of pseudo oracle. It is also referred to as dual-coding and used in higly critical software. (Weyuker and automatic system testing of programs without test oracles: Christian murphy, kuang shen). Pseudo-oracles are multiple implementation of same specification of the original program under test.
 However dual coding comes with it's own set of problems. As [this and this ] pointed out that it 
 multiple implementation may not exist
 multiple implementation may be created by the same or same set of developers prone to make same mistakes.
 pseudo-oracle requires at least two implementation and it may be a lot of overhead 
 The authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

 Although non-testable programs occur in all areas of data processing, the problem is undoubtedly most acute in the area of numerical computations, particularly where floating point arithmetic is used. While performing mathematical computations, errors from three sources can creep in:
\begin{enumerate}
  \item The mathematical model used to do the computations.
  \item Programs written to implement the computation.
  \item The features of the environment like round-off, floating point operations etc.
\end{enumerate}

Many techniques have since been developed to develop these set of non-testable programs.

Two ways to deal with uncertainty are to exercise more control over the inputs provided to the unit under test and to constrain the testing environment. Some uncertainties like those present in systems that deal with the physical world are aleatoric; that is, they cannot be known precisely because of their inherent variability and noise.  Epistemic uncertainties are those that could be resolved with enough effort (e.g., over-engineering a sensor-based system to minimize inference errors about the environment)— and resolving them are becoming more numerous and costly, as the systems are becoming increasingly complex. A complementary way to deal with uncertainty at the other end of the testing process is to develop more sophisticated oracles. If the oracles are relaxed too much to tolerate the variations introduced by uncertainties, there is an inherent risk for the uncertain behavior to mask a fault. On the other hand, if the oracles are too narrow it may cause them to generate false positives, resulting in wasted developer's time. The authors provide a set of requirements for adequate handling of uncertainty in testing:
\begin{enumerate}
  \item Specifying input distributions and generating inputs with the help of the distributions instead of using discrete inputs.
  \item Probabilistic oracles that can help distinguish acceptable from unacceptable misbehaviors. These models will also provide the specification of the likelihood of results.
  \item Richer models to represent system and environment uncertainty, so that uncertainties can be connected to test requirements and outcomes. This will help with automated uncertainty quantification.
\end{enumerate}
Not all systems will impose these requirements, and not all techniques will satisfy them. In fact, they expect it will be necessary to develop a suite of techniques for dealing with uncertainty, selected according to system characteristics and the particular forms of uncertainty the system embodies and based on the use of stochastic models and quantitative analyses.

\section{On Testing Non-testable Programs \cite{Weyuker}}

 But, due to a great deal of overhead involved pseudo-oracles may not be practical for every situation. 
A different, and frequently employed course of action is to run the program on 'simplified' data for which the correctness of the results can be accurately and readily determined. The tester then extrapolates from the correctness of the test results on these simple cases to correctness for more complicated cases. In this case, we are deliberately omitting test cases even though these cases may have been identified as important. They are not being omitted because it is not expected that they will yield substantial additional information, but rather because they are impossible, too difficult, or too expensive to check. The problem with using simple test cases is very obvious i.e. it is common for central cases to work perfectly whereas boundary cases to cause errors.

Even in the absence of oracles the users often have a ballpark idea of what the correct answer would look like without knowing the correct answer. In such cases, we make use of partial oracles. It is relatively easier to test the systems on simpler inputs for which the output is known. There is rarely a single correct answer in these types of computations. Rather, the goal is generally an approximation which is within a designated tolerance of the exact solution. The authors finally make five recommendation for items to be considered as a part of documentation during testing.
\begin{enumerate}
  \item The criteria used to select the test data.
  \item The degree to which the criteria were fulfilled.
  \item The test data, the program ran on.
  \item The output of each of each test datum.
  \item How the results were determined to be correct or acceptable.
\end{enumerate}
Although these recommendations do not solve the problem of non-testable programs, however, they do provide information on whether the program should be considered adequately tested or not.

### 2019-08-04 chapters/litReview/metamorphicTesting.tex
Updates from Overleaf

\section{Metamorphic Testing}
	\subsection{A Survey on Metamorphic Testing \cite{Segura2016}}
		Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer four important research questions:
		\begin{enumerate}
			\item RQ1: What improvements to the technique have been made?
			\item RQ2: What are its known application domains?
			\item RQ3: How are experimental evaluations performed?
			\item RQ4: What are the future research challenges?
		\end{enumerate}

>>>>

Zhou et al. (Metamorphic Testing and Its Applications ∗ † Zhi Quan Zhou‡∥, D.H. Huang‡, T.H. Tse§,
Zongyuan Yang ¶, Haitao Huang ¶, and T. Y. Chen ‡) argued that successful test cases

Chen, Cheung, and Yiu (1998) first introduced the idea of metamorphic testing to answer the oracle problem.
Segura et al. did an extensive review of metamorphic testing with 119 papers published between 1998 and 2015 to answer important research questions about origin, current state, and, future of metamorphic testing.
% \begin{enumerate}
% 	\item RQ1: What improvements to the technique have been made?
% 	\item RQ2: What are its known application domains?
% 	\item RQ3: How are experimental evaluations performed?
% 	\item RQ4: What are the future research challenges?
% \end{enumerate}

\section{Metamorphic Testing}
	\subsection{A Survey on Metamorphic Testing \cite{Segura2016}}

### 2019-08-04 chapters/methodology/collection.tex
Updates from Overleaf

\section{Setting up the Test Environment}
% \subsection{Docker}
% For replication of results. Image can be downloaded from dockerhub. Attached volume for persisting data.
\subsection{Jupyter}
The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc. by allowing us to create and share documents that contain live code, equations, visualizations and narrative text. Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.). The Jupyter notebook combines two components:
\begin{itemize}
  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, the codes are written in python notebook which can be accessed from http://github.com/.

@@

\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 60,000 examples, and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits. The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

\subsubsection{Format of Dataset}
The data is stored in a very simple file format designed for storing vectors and multidimensional matrices. All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors. There are 4 files:
\begin{itemize}
  \item train-images-idx3-ubyte: training set images
  \item train-labels-idx1-ubyte: training set labels
  \item t10k-images-idx3-ubyte:  test set images
  \item t10k-labels-idx1-ubyte:  test set labels
\end{itemize}
The format of training and test files are described in the following table.
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of items \\
\hline
0008  &   unsigned byte  & ??          &     label \\
\hline
0009  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
\hline
\end{tabular}
\caption{Training data file format.}
\label{tbl:training-file-format}
\end{table}

@@

\subsection{EMNIST Dataset}
The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
and converted to a 28x28 pixel image format and dataset structure that directly matches the MNIST dataset.

\subsubsection{Dataset Summary}
There are six different splits provided in this dataset. A short summary of the dataset is provided below:
\begin{itemize}
  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
  \item EMNIST MNIST: 70,000 characters. 10 balanced classes.
\end{itemize}
The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task. The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.

>>>>

\section{Tools}
\subsection{Jupyter}
The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc. by allowing us to create and share documents that contain live code, equations, visualizations and narrative text. Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.). The Jupyter notebook combines two components:
\begin{itemize}
  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, the codes are written in python notebook which can be accessed from http://github.com/.

@@

\section{Algorithm}
\subsection{Convolutional neural network}
\subsection{2-layer neural network}

\section{Dataset}
\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 55,000 examples, and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits. The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

\subsection{EMNIST Dataset}
The EMNIST dataset is a set of handwritten character digits derived from the NIST Special Database 19
and converted to a 28x28 pixel image format. The EMNIST dataset structure directly matches the MNIST dataset.

\subsubsection{Dataset Summary}
There are six different splits provided in this dataset. A short summary of the dataset is provided below:
\begin{itemize}
  \item EMNIST ByClass: 814,255 characters. 62 unbalanced classes.
  \item EMNIST ByMerge: 814,255 characters. 47 unbalanced classes.
  \item EMNIST Balanced:  131,600 characters. 47 balanced classes.
  \item EMNIST Letters: 145,600 characters. 26 balanced classes.
  \item EMNIST Digits: 280,000 characters. 10 balanced classes.
  \item EMNIST MNIST: 65,000 characters. 10 balanced classes.
\end{itemize}
The full complement of the NIST Special Database 19 is available in the ByClass and ByMerge splits. The EMNIST Balanced dataset contains a set of characters with an equal number of samples per class.
The EMNIST Letters dataset merges a balanced set of the uppercase and lowercase letters into a single 26-class task. The EMNIST Digits and EMNIST MNIST dataset provide balanced handwritten digit datasets directly compatible with the original MNIST dataset.

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/digit.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/letter.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Fashion MNIST Dataset}
Fashion-MNIST is a dataset of Zalando's article images—consisting of a training set of 55,000 examples and a test set of 10,000 examples. Each example is a 28x28 grayscale image, associated with a label from 10 classes.

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Label} & \textbf{Description} \\ \hline
0  &   T-shirt/top \\ \hline
1  &   Trouser \\ \hline
2   &	Pullover \\ \hline
3   &	Dress \\ \hline
4   &	Coat \\ \hline
5   &	Sandal \\ \hline
6   &	Shirt \\ \hline
7   &	Sneaker \\ \hline
8   &	Bag \\ \hline
9   &	Ankle boot \\ \hline
\end{tabular}
\caption{Data file format.}
\label{tbl:training-file-format}
\end{table}

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/fashion.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Format of Dataset}
The data is stored in a very simple file format designed for storing vectors and multidimensional matrices. All the integers in the files are stored in the MSB first (high endian) format used by most non-Intel processors. There are 4 files:
\begin{itemize}
  \item train-images-idx3-ubyte: training set images
  \item train-labels-idx1-ubyte: training set labels
  \item t10k-images-idx3-ubyte:  test set images
  \item t10k-labels-idx1-ubyte:  test set labels
\end{itemize}
The format of training and test files are described in the following table.
\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{offset} & \textbf{type}    &      \textbf{value}    &      \textbf{description} \\
\hline
0000  &   32 bit integer & 0x00000801(2049) & magic number (MSB first) \\
\hline
0004  &   32 bit integer & 60000       &     number of items \\
\hline
0008  &   unsigned byte  & ??          &     label \\
\hline
0009  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{........}} \\
\hline
xxxx  &   unsigned byte  & ??          &     label \\
\hline
\multicolumn{4}{|c|}{\textbf{The label values are 0 to 9.}} \\
\hline
\end{tabular}
\caption{Training data file format.}
\label{tbl:training-file-format}
\end{table}

@@

% \subsection{Docker}
% For replication of results. Image can be downloaded from dockerhub. Attached volume for persisting data.

### 2019-08-04 chapters/results/results.tex
Updates from Overleaf

\section{Overall Accuracy}
\begin{figure}
  \includegraphics[width=\linewidth]{images/rotation}
  \caption{MR: Rotation.}
  \label{fig:rotation 1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shade}
  \caption{MR: Shading.}
  \label{fig: Shading}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/sheer}
  \caption{MR: Sheering.}
  \label{fig: Sheer}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shift}
  \caption{MR: Shifting.}
  \label{fig: Shift}
\end{figure}

\section{Digit-by Accuracy}
\begin{figure}
  \includegraphics[width=\linewidth]{images/rotation1}
  \caption{MR: Rotation.}
  \label{fig:rotation 1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shade1}
  \caption{MR: Shading.}
  \label{fig: Shading}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/sheer1}
  \caption{MR: Sheering.}
  \label{fig: Sheer}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shift1}
  \caption{MR: Shifting.}
  \label{fig: Shift}
\end{figure}

>>>>

\section{Effect of transformation on model}
From literature review we postulate that small changes to input image should not affect the prediction model. In this thesis we investigate the effect of the identified metamorphic properties have on the accuracy of model. For each machine learning algorithms generated ten models . For each metamorphic property identified in section X we look how it affects . We calculated the following metrics to evaluate the affect of metamophic relations on deep-learning algorithm. To tackle the non-deterministic nature of training a neural network model, we ran each of the above experiment ten times and calculated average.
\subsection{Overall Accuracy or true positive}
    Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made.
\subsection{Digit-by Accuracy or true positive for each digit}
    We analyze each digit and 
\subsection{Misclassification of digits}
    In order to see how each digit is affected by changes in  mp. For each digit 0-9 we calculated the number of correct predictions made by the model as compared to total number of .
\subsection{Robustness}

\clearpage
% \input{CNN/Rotate/rotate.tex}
\section{Overall Accuracy}
\begin{figure}[htb!]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Rotate/acc.png}
        \caption{Rotation}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{ 0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Shade/acc.png}
        \caption{Shading}
        \label{fig:Rotate-misclass1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/Shear/acc.png}
        \caption{Shearing}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/ShiftX/acc.png}
        \caption{Shifting in X-axis}
        \label{fig:Rotate-misclass0}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{chapters/results/CNN/ShiftY/acc.png}
        \caption{Shifting in Y-axis}
        \label{fig:Rotate-misclass0}
    \end{subfigure}s
    \caption{Accuracy graphs for convolutional neural network.}
    \label{fig:Rotate-misclassifications}
\end{figure}

\clearpage
\input{digit-by-accuracy.tex}

\iffalse
Number of instances of each digit: 1000000 \\
Confusion Matrix for rotation
Rotate
\begin{table}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
935597 & 1571 & 6922 & 1439 & 12189 & 14037 & 6591 & 1488 & 9736 & 10430 \\ \hline
2156 & 681401 & 46519 & 2751 & 169826 & 27931 & 9759 & 3613 & 45566 & 10478 \\ \hline
48251 & 14436 & 625369 & 14254 & 92329 & 14828 & 21352 & 51716 & 68410 & 49055 \\ \hline
55511 & 924 & 27210 & 641320 & 49224 & 79421 & 24213 & 9285 & 45419 & 67473 \\ \hline
14679 & 7786 & 82089 & 3506 & 626526 & 22201 & 29658 & 9793 & 74675 & 129087 \\ \hline
36982 & 851 & 3881 & 20562 & 41609 & 658850 & 100751 & 8549 & 32895 & 95070 \\ \hline
14801 & 5076 & 5850 & 2183 & 21595 & 43878 & 881633 & 61 & 24041 & 882 \\ \hline
19761 & 41054 & 89028 & 12815 & 37202 & 7157 & 1548 & 604877 & 25560 & 160998 \\ \hline
44287 & 3357 & 18687 & 7605 & 99678 & 27689 & 47153 & 8077 & 664412 & 79055 \\ \hline
19214 & 3572 & 22930 & 7800 & 64705 & 32264 & 3295 & 26788 & 34992 & 784440 \\ \hline
\end{tabular}
\end{table}

Shade
\begin{table}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
723812 & 170554 & 42780 & 6728 & 9156 & 22649 & 14219 & 4105 & 1688 & 4309 \\ \hline
254 & 962044 & 2730 & 390 & 2949 & 583 & 28386 & 869 & 1590 & 205 \\ \hline
5878 & 186546 & 756806 & 7351 & 5673 & 6460 & 12743 & 9246 & 6682 & 2615 \\ \hline
7909 & 197655 & 25332 & 704395 & 3671 & 26024 & 13630 & 7059 & 7924 & 6401 \\ \hline
980 & 199247 & 17353 & 83 & 736257 & 5919 & 10603 & 1859 & 4639 & 23060 \\ \hline
1759 & 185772 & 11045 & 12420 & 13794 & 736958 & 17460 & 3035 & 6985 & 10772 \\ \hline
1724 & 187885 & 29599 & 627 & 7308 & 8158 & 762263 & 73 & 2267 & 96 \\ \hline
1038 & 230118 & 7008 & 4753 & 6887 & 4707 & 1820 & 711488 & 7578 & 24603 \\ \hline
6249 & 220252 & 25119 & 7814 & 19723 & 37098 & 17413 & 4407 & 644767 & 17158 \\ \hline
3420 & 216638 & 6303 & 1732 & 48951 & 9704 & 3905 & 25036 & 11315 & 672996 \\ \hline
\end{tabular}
\end{table}

 Shear
\begin{table}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
843745 & 10901 & 25910 & 6041 & 22737 & 31418 & 18795 & 6279 & 25431 & 8743 \\ \hline
489 & 827503 & 75423 & 1064 & 42026 & 5999 & 4750 & 4074 & 35602 & 3070 \\ \hline
5078 & 18985 & 841933 & 16944 & 20220 & 8561 & 24028 & 14614 & 45286 & 4351 \\ \hline
9944 & 9350 & 32310 & 764503 & 48583 & 73988 & 13401 & 4440 & 28001 & 15480 \\ \hline
9834 & 5379 & 38067 & 1622 & 780726 & 4660 & 19143 & 3798 & 28973 & 107798 \\ \hline
6990 & 7222 & 17568 & 15686 & 38861 & 840605 & 17008 & 1864 & 24632 & 29564 \\ \hline
7975 & 4004 & 23667 & 1264 & 22961 & 18252 & 902574 & 472 & 18495 & 336 \\ \hline
1905 & 83886 & 71323 & 13684 & 28050 & 4143 & 2944 & 699486 & 29394 & 65185 \\ \hline
8266 & 24716 & 60365 & 5607 & 47917 & 15477 & 21918 & 8603 & 782538 & 24593 \\ \hline
4575 & 17714 & 27060 & 5122 & 117887 & 14337 & 1801 & 34062 & 38993 & 738449 \\ \hline
\end{tabular}
\end{table}

 ShiftX
\begin{table}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
77949 & 614059 & 82304 & 114994 & 10084 & 27145 & 16921 & 37383 & 15310 & 3851 \\ \hline
18598 & 762514 & 11391 & 108735 & 21327 & 19628 & 14301 & 40521 & 1593 & 1392 \\ \hline
5413 & 596299 & 158838 & 111720 & 8599 & 65944 & 29801 & 18278 & 3585 & 1523 \\ \hline
1960 & 613767 & 48437 & 192270 & 15577 & 60280 & 19406 & 37799 & 8608 & 1896 \\ \hline
10748 & 606441 & 25128 & 115124 & 143172 & 26096 & 9445 & 52487 & 2675 & 8684 \\ \hline
3280 & 576218 & 57996 & 123105 & 7793 & 122565 & 13449 & 83188 & 7653 & 4753 \\ \hline
6802 & 629739 & 79954 & 107383 & 11197 & 39254 & 112765 & 9497 & 1752 & 1657 \\ \hline
4431 & 612470 & 14042 & 104293 & 6656 & 54982 & 3929 & 188195 & 3754 & 7248 \\ \hline
11402 & 604142 & 33747 & 119427 & 14964 & 36848 & 10922 & 73575 & 84225 & 10748 \\ \hline
6458 & 610597 & 17436 & 112603 & 24052 & 23167 & 3885 & 108416 & 9620 & 83766 \\ \hline
\end{tabular}
\end{table}

 ShiftY
\begin{table}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
66197 & 542587 & 43176 & 106135 & 42382 & 12674 & 70021 & 78999 & 1631 & 36198 \\ \hline
538 & 725379 & 4939 & 111517 & 12744 & 23113 & 33750 & 63499 & 898 & 23623 \\ \hline
5931 & 549369 & 84027 & 122009 & 46036 & 29879 & 50616 & 84857 & 1755 & 25521 \\ \hline
5459 & 536243 & 48175 & 173095 & 19257 & 21261 & 57625 & 90112 & 1912 & 46861 \\ \hline
5912 & 587840 & 31183 & 111527 & 72612 & 18906 & 56932 & 95170 & 958 & 18960 \\ \hline
4400 & 549322 & 56501 & 108096 & 14913 & 68901 & 55441 & 99507 & 4262 & 38657 \\ \hline
4196 & 569875 & 38726 & 108298 & 22672 & 11800 & 106513 & 75694 & 1169 & 61057 \\ \hline
6315 & 586659 & 32610 & 115134 & 43765 & 29717 & 47371 & 119460 & 1436 & 17533 \\ \hline
15388 & 533073 & 30139 & 108200 & 16740 & 19676 & 83688 & 80939 & 50348 & 61809 \\ \hline
13355 & 566917 & 27002 & 109136 & 20624 & 17805 & 81323 & 95899 & 1001 & 66938 \\ \hline
\end{tabular}
\end{table}

\fi

\clearpage

To generate new data from MNIST digit dataset. While using rotation 0 should be in a prticular range. 1 should be in particular range.....
